SVG: The Paper

### 2022-04-13 Analysis/index.Rmd
trial level plot nearly working

```{r, message=FALSE}
# attach packages
library(tidyverse)
library(patchwork)
library(tidybayes)
```

```{r}
# set ggplot2 options
theme_set(ggthemes::theme_tufte() + theme(plot.background = element_rect(fill = "grey95", colour = "grey95")))

@@

```{r, echo = TRUE}
# item weights pre-computed - see xxxxx.R
a <- readRDS("scratch/qjep_model_weights.rda") %>%
  filter(found != 1) # remove initial selections

@@

```{r, echo = TRUE}
summary(lm(accuracy ~ condition * bP, fit))
```

# Initial Selection

## QJEP Dataset

```{r}
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))

ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
  facet_wrap(~observer)

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
plt_x + plt_y
```

## Tagu dataset

```{r}
d <- read_csv("data/tagu_2020_prox_mouse.csv", show_col_types = FALSE) %>%
  filter(found == 1) %>%
  mutate(condition = as_factor(condition))

ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
  facet_wrap(~observer)

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) #+
  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
plt_x + plt_y
```

>>>>

```{r, message=FALSE}
# attach packages
library(tidyverse)
library(patchwork)
library(tidybayes)
library(ggrepel)
```

```{r}
# set ggplot2 options
theme_set(ggthemes::theme_tufte() + theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))

# some more colours
#Isfahan2 = list(c("#d7aca1", "#ddc000", "#79ad41", "#34b6c6", "#4063a3"), c(4, 2, 3, 5, 1), colo

@@

```{r, echo = TRUE}
# read in data
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  mutate(condition = as_factor(condition),
         condition = fct_recode(condition, feature = "1", conjunction = "2"),
         targ_type = as_factor(targ_type))

# item weights pre-computed - see xxxxx.R
a <- readRDS("scratch/qjep_model_weights.rda") %>%
  filter(found != 1) # remove initial selections

@@

```{r, echo = TRUE}
summary(lm(accuracy ~ condition * bP, fit))
```
### Examples of Trials

Let's score every trial by how well the model captures behaviour, and then plot some different examples

```{r, echo = TRUE}
a %>% group_by(observer, condition, trial) %>% 
  summarise(prop_max = mean(selected_max), .groups = "drop") %>% 
  arrange(desc(prop_max)) %>%
  ungroup() -> a_trl
```

```{r, fig.cap = "Histogram of how predictiable indivuidual trials are, defined as how often the model assigned the largest weight to the target that was then selected."}
ggplot(a_trl, aes(prop_max)) + 
  geom_histogram(fill = "#34b6c6", breaks = seq(0, 1, 0.025)) +
  scale_x_continuous("trial predictability")
```

Let's plot some examples oh highly predictable (top 5%), and unpredictable (bottom 5%) trials.

```{r, echo = TRUE}
qs <- quantile(a_trl$prop_max, c(0.05, 0.95))

trls_hard <- filter(a_trl, prop_max < qs[1]) %>% sample_n(3)
trls_easy <- filter(a_trl, prop_max > qs[2]) %>% sample_n(3)

# 
source("plot_trial.R")

plts <- map(1:3, plot_trial, trls_easy, a, d)

#plts[1] + plts[2] + plts[3]

plot(plot_trial(1, trls_hard, a, d))

```
